---
title: "Tutorial 2"
author: "Chen Jiesheng (A0099515U)"
date: "2016─Ж1н┬29╚Н"
output: html_document
---


```{r,message=FALSE,echo=FALSE}
library(ggplot2)
library(dplyr)
```
1. (a) For Waiting Time:
```{r, echo=FALSE}
labs <- read.csv("~/labs.csv")
median(labs$WaitTime)
hist(labs$WaitTime)
```

For Service Satisfaction
```{r,echo=FALSE}

count(labs, SvcSat)
a<-prop.table(table(labs$SvcSat))
a[2]
barplot(table(labs$SvcSat))
```

(b) Is there any statistical evidence to suggest differences in service satisfaction for age and gender?

For age:
```{r,echo=FALSE}
barplot(table(labs$SvcSat,labs$AGE), beside=TRUE, legend=rownames(table(labs$SvcSat,labs$AGE)))
```
From the graph above, the aged populations are more likely to be unsatisfied.

For gender:
```{r,echo=FALSE}
barplot(table(labs$SvcSat,labs$Gender), beside=TRUE, legend=rownames(table(labs$SvcSat,labs$Gender)))
```
Gender wise, males are more likely to be unsatisfied.

Statistical Evidence:
```{r,echo=FALSE}
var1 <- ifelse(labs$SvcSat=="Y",1,0) 
var2 <- ifelse(labs$Gender=="M",1,0)
var3 <- labs$AGE
lm(var1~var2+var3)
summary(lm(var1~var2+var3))
```
However, the differences with gender is insignificant as shown above.

(C)
```{r,echo=FALSE}
var4 <- ifelse(labs$SvcSat=="Y",1,0)
cor(labs$WaitTime,var4)
```
Hence, the longer the waiting time, the more dissatisfied customers will be.

(d)
```{r,echo=FALSE}
test = mutate(labs,bmi=WT/(HT*HT))
c = select(test,17,13)
c = na.omit(c)
var5=as.numeric(levels(c$TC)[c$TC])
cor(c$bmi, var5)
```

(e)
```{r,echo=FALSE}
test = mutate(labs,bmi=WT/(HT*HT))
c=select(test,17,1,5,6,11,13)
c=na.omit(c)
var1 <- ifelse(c$ETHNIC=="C",1,0)
var2 <- ifelse(c$Gender=="M",1,0)
lm(c$bmi~var1+var2+c$AGE+c$SBP+c$TC)
summary(lm(c$bmi~var1+var2+c$AGE+c$SBP+c$TC))
```
From above, we will know that the BMI = (-0.78888)*1+1*(0.06513)+45*0.02346+0.06053*135+0.03927*150 = 14.394
The assumption is that our model is correct and representative.

(a)
```{r,echo=FALSE}
B = matrix( c(3, 4, 7, 2), nrow=2, ncol=2)
colnames(B) <- c("Diabetic Complications Present","Diabetic Complications Absent")
rownames(B) <- c("Diabetic Control Good","Diabetic Control Poor")
prop.table(B,1)
```
From above table, indeed it is different.

(b)
```{r,echo=FALSE}
t.test(prop.table(B,1)[,1],prop.table(B,1)[,2])
prop.test(B,correct=FALSE)
```

(c) Pearson's chi-squared test (до2) is a statistical test applied to sets of categorical data to evaluate how likely it is that any observed difference between the sets arose by chance.

Since there are no categorical data in this matrix, chi-squired test is not applicable.