---
title: "tut5"
author: "Chen Jiesheng (A0099515U)"
date: "2016Äê2ÔÂ25ÈÕ"
output: md_document
---
Chen Jiesheng (A0099515U)

```{r,message=FALSE,echo=FALSE}
library(Rcmdr)
library(car)
library(RcmdrMisc)
library(foreign, pos=20)
```

```{r}
country <- read.spss(file="country122.sav", use.value.labels=TRUE, max.value.labels=Inf, to.data.frame=TRUE)
colnames(country) <- tolower(colnames(country))
```

```{r}
reg1 <- lm(lifeexpf~birthrat, data=country)
summary(reg1)
```
Given that the p-value is smaller than 0.05, it is statistically significant that there is a linear relationship between life expectancy and birth rate.

R-square is 75.4%, so the relationship is pretty strong.

```{r}
scatterplot(lifeexpf~birthrat, reg.line=lm, boxplots=FALSE, data=country)
```

Hence, the simple linear equation is life expectancy = -0.74471 * birth rate + 89.58892

Given birthrate of 25 livebirths per 1000 population, life expectancy = 
```{r}
-0.74471 * 0.025 + 89.58892
```

The assumptions are that birthrate given is representative to the population birthrate, not anomaly.